{ \fontfamily{ptm}\selectfont Nesterov's First Order Method Accelerations: Unification, Applications and Numerical Experiments }

### 2025-02-14 Notebook LaTEX/Proposal/proposal.tex
>w<, fix cringe shit

        They generalize many existing sequences used in accelerated proximal gradient schemes. 
        This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
        This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
        The table below shows the R-WAPG convergence results specialized into various settings. 

@@

@@

@@

    \subsection{Future works for R-WAPG}
        The R-WAPG framework neglected a detail in the literatures. 
        Our future works would extend the frameworks and include this detail. 
        \subsubsection{Nesterov's idea of strong convexity transfer}
            We consider the case that $F = f + g$ where, $f$ is $L$ Lipschitz smooth, $\mu_f \ge 0$ strongly convex and $g$ is closed convex. 
            In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex. 
            \par
            This detail on itself is not necessarily interesting, since without lost of generality, we can always do the splitting $f + \mu_\Psi/2 \Vert \cdot\Vert^2$ and $\Psi - \mu_\Psi/2\Vert \cdot\Vert^2$ instead so that the smooth part is $\mu_\Psi \ge 0$ strongly convex. 
            It's an interesting detail we should consider because: 
            \begin{enumerate}
                \item A strongly convex nonsmooth parts still gives linear convergence by Theorem 6 in Nesterov's 2013 \cite{nesterov_gradient_2013}. 
                \item The strong convexity constant can be easily estimated via a routine specified as (5.14) in Nesterov 2013 \cite{nesterov_gradient_2013} and the complexity of the estimation is bounded precisely. 
            \end{enumerate}
            (i) indicates that our theories of R-WAPG is incomplete, since it doesn't predict linear convergence when $g$ is strongly convex. 
            (ii) indicates that splitting the strongly convex objective so that it's with the proximal operator gives computational advantage. 
            \par
            Furthermore, Nesterov was not the only person who thought about it.
            In Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA, and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex. 
            \par
            Upon first inspection and preliminary readings, we lay out the followings that may contribute to include strong convexity in the non-smooth part into our R-WAPG framework. 
            The R-WAPG sequence $\alpha_k, \rho_k$ will have to describe the sequence in Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5 which has 
            \begin{align*}
                q \alpha_{k + 1}^2 &= (1 - \alpha_{k + 1})q\alpha_k^2 + q \alpha_{k + 1}^2. 
            \end{align*}
            Where $q = L^{-1}(\mu_f + \mu_g)/(1 + L^{-1}\mu_g)$. 
            Additionally, observe that in the special case where $f \equiv 0$, then proximal gradient becomes proximal point on the strongly convex objective $\mu_g \ge0$ alone and its convergence rate is included in the outer loop convergence analysis in the Catalyst Acceleration Framework by Lin et al. \cite{lin_universal_2015}, this provided us with a hint on an estimating sequence approach. 
            Of course, Lemma \ref{thm:prox-grad-ineq} requires a complete rework to include $\mu_g \ge0$. 
            The recursive quantity $R_k$ would also require a complete rework because we invented the quantity $R_k$ just so the proof of Proposition \ref{prop:stepwise-lyapunov} falls through. 
            The quantity is obtained from the Nesterov's estimating sequence of APG, to include such a change, the estimating sequence required to engineer $R_k$, which is the recursive quantity will also require rework. 
            The only part that may not require rework is the Definition \ref{def:stepwise-wapg} because the R-WAPG sequence is generic. 
            We are quite certain about these required changes to achieve the open question because we invented R-WAPG.

@@

            Their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 
            Finally, it's worth noting that in the years before and after Necoara et al.'s paper and Catalyst, there were parallel developments around the ideas of extending Nesterov's accelerations and Catalyst to the nonconvex settings. 
            Paquette et al. \cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges. 

@@

            There are three pillars that supported Catalyst Accelerations: 

@@

            The class of weakly convex function is particularly interesting because it has convergance claim of the gradient norm in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}. 
            It's unclear how their convergence theories can be combined with NAG in the non-convex case, but it's worth investigating. 

>>>>

        They generalize existing sequences used in accelerated proximal gradient schemes. 
        Choosing the sequence $\alpha_k, \rho_k$ with some specific rules, it yields convergence results found in the literatures for Euclidean variants of FISTA. 
        Table \ref{table:unify-nag-results} shows convergence results specialized to some FISTA variants found in the literatures. 

@@

            \caption{Table showing the results of this section.}
            \label{table:unify-nag-results}

@@

        Using the above lemma about R-WAPG sequence, it can derive the convergence rate of a FISTA variable proposed by Chambolle, Dossal \cite{chambolle_introduction_2016}. 
        Following a similar pattern, the lemma follows characterize a constant sequence of $\alpha_k, \rho_k$ for the R-WAPG sequences which enable us to characterize the linear convergence rate of all $\mu > 0$ strongly convex function with a fixed momentum parameter. 

@@

    \subsection{Future works for R-WAPG}
        The R-WAPG framework neglected a detail in the literatures. 
        Our future works would extend the frameworks and include this detail. 
        \subsubsection{Nesterov's idea of strong convexity transfer}
            We consider the case that $F = f + g$ where, $f$ is $L$ Lipschitz smooth, $\mu_f \ge 0$ strongly convex and $g$ is closed convex. 
            In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex. 
            Here would be our question: 
            \begin{quote}
                Is it possible to include the a $\mu_\Psi$ into our R-WAPG framework? 
            \end{quote}
            \par
            Without lost of generality, we can always do the splitting $f + \mu_\Psi/2 \Vert \cdot\Vert^2$ and $\Psi - \mu_\Psi/2\Vert \cdot\Vert^2$ instead so that the smooth part is $\mu_\Psi \ge 0$ strongly convex. 
            It's an interesting detail we should consider including because: 
            \begin{enumerate}
                \item A strongly convex nonsmooth parts still gives linear convergence by Theorem 6 in Nesterov's 2013 \cite{nesterov_gradient_2013}. 
                \item The strong convexity constant can be easily estimated via a routine specified as (5.14) in Nesterov 2013 \cite{nesterov_gradient_2013} and the complexity of the estimation is bounded precisely. 
            \end{enumerate}
            (i) indicates that our theories of R-WAPG is incomplete, since it doesn't predict linear convergence when $g$ is strongly convex. 
            (ii) indicates that splitting the strongly convex objective so that it's with the proximal operator gives computational advantage. 
            \par
            Besides Nesterov's contributions, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA In Algorithm 5.
            They assumed $F = f + g$ with $f, g$ being strongly convexity with constants $\mu_f \ge 0, \mu_g \ge 0$ respectively so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex. 
            \par
            Upon first inspection and preliminary readings, we lay out the followings that may contribute to include strong convexity in the non-smooth part into our R-WAPG framework. 
            The R-WAPG sequence $\alpha_k, \rho_k$ will have to describe the sequence in Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5 which has 
            \begin{align*}
                q \alpha_{k + 1}^2 &= (1 - \alpha_{k + 1})q\alpha_k^2 + q \alpha_{k + 1}^2. 
            \end{align*}
            Where $q = L^{-1}(\mu_f + \mu_g)/(1 + L^{-1}\mu_g)$. 
            Additionally, observe that in the special case where $f \equiv 0$, then proximal gradient becomes proximal point on the strongly convex objective $\mu_g \ge0$ alone and its convergence rate is included in the outer loop convergence analysis in the Catalyst Acceleration Framework by Lin et al. \cite{lin_universal_2015}, this provided us with a hint on an estimating sequence approach. 
            Of course, Lemma \ref{thm:prox-grad-ineq} requires a complete rework to include $\mu_g \ge0$. 
            The recursive quantity $R_k$ would also require a complete rework because we invented the quantity $R_k$ just so the proof of Proposition \ref{prop:stepwise-lyapunov} falls through. 
            The quantity is obtained from the Nesterov's estimating sequence of APG, to include such a change, the estimating sequence required to engineer $R_k$, which is the recursive quantity will also require rework. 
            The only part that may not require rework is the Definition \ref{def:stepwise-wapg} because the R-WAPG sequence is generic. 
            We are quite certain about these required changes to achieve the open question because we invented R-WAPG.

@@

            Hence, this is what we would describe the open question to be: 
                Can we extend the linear convergence results of inner loop or outer loop of Catalyst Acceleration into settings weaker than strong convexity (Potentially nonconvex)? 
            In the coming parts, we will focus on developments in the literatures adjacent to the open question above. 
            Objectives will be summarized at the end. 
            There were parallel developments around the ideas of Nesterov's accelerations and Catalyst in the nonconvex settings during the years before Necoara et al.'s paper and Catalyst to current date. 
            Paquette et al. \cite{paquette_catalyst_2018} were inspired by Ghadimi \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges. 

@@

            Now that the scope had been settled, let's consider major components of Catalyst Acceleration where extensions to the nonconvex settings can be made. 
            There are three pillars that support Catalyst Accelerations: 

@@

            The class of weakly convex function is particularly interesting because it has convergence claim of the gradient norm in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}. 
            It's unclear how their convergence theories can be combined with NAG in the nonconvex case, but it's worth investigating. 
            Finally, we can summarize a rough sketch of ideas to explore that will assist the open question we posed. 
                \item Does the convergence results modestly extend to the non-strongly convex settings described by Necoara \cite{necoara_linear_2019} et al.? 
                \item Is it possible to extend the Nesterov's acceleration to non-convex settings such as convergence of gradient norm as described in Ghadimi \cite{ghadimi_accelerated_2016} without restarting? If so, what are the trade offs here if we wish to attain stronger convergence claims on the final iterates, or the function value? 
                \item Do there exist a way of extending inexact proximal point method to the nonconvex settings that also include Nesterov's acceleration? 
